Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2023-01-09 supplement.tex
clarifications in supp

@@

Finally, many features of recent human history were consistently parameterized
across each of our tested models (such as recent migration rates and population
sizes). We evaluated the consistency of these recent parameters across our
different models (Figure~\ref{fig:supp-bootstrap-overlap}). In the case that
the model provides a very poor fit to the data (the single origin model) the
CIs of some parameters do not overlap with those of the other models (e.g.,
Mende population sizes, and some migration rates). Many parameters are largely
consistent across each of the models, showing that inferences of recent history
are largely robust to the details of population structure in the distant past.

>>>>

A simulation-based validation of the confidence interval calculation is provided in Section 
\ref{sec:confidence-intervals}.

@@

Finally, many features of recent human history were consistently parameterized
across each of our tested models (such as recent migration rates and population
sizes). We evaluated the consistency of these recent parameters across our
different models (Figure~\ref{fig:supp-bootstrap-overlap}). Since all models use 
the same set of bootstrapped simulations, systematic differences between models 
reflect the effect model specification rather than statistical uncertainty. The effects 
of statistical uncertainty of model specifications need not be of the same order, but 
we find it useful to compare the two sources of uncertainties. Because model 
specification differences are mostly in the distant past, we expect to find more 
differences caused by model specifications in the distant past.
Many recent parameters are largely
consistent across each of the models, showing that inferences of recent history
are largely robust to the details of population structure in the distant past.
The model that provides a very poor fit to the data (the single origin model) shows 
stronger model specification effects even for recent parameters (e.g.,
Mende population sizes, and some migration rates).
